Lyman-alpha spectra from rotating outflows

### 2017-10-16 paper/paper.tex
change figsize
minor updates

In this paper we introduce first our theoretical tools and assumptions
in Section \ref{sec:theory}, then we present the numerical results and
comparisons against the analytical solution in \ref{sec:results}.
In Section \ref{sec:discussion} we discuss our results and their
possible implications for observational analysis to finally present
our conclusions in Section \ref{sec:conclusions}.

@@

% Esta figura deberia tener 3 x 3 vinetas. vout=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vrot=0, | tau=1E5, vrot=50, | tau=1E5, vrot=100, 
% |tau=1E6, vrot=0, | tau=1E6, vrot=50, | tau=1E6, vrot=100, 
% |tau=1E7, vrot=0, | tau=1E7, vrot=50, | tau=1E7, vrot=100, 
\begin{figure}
	\begin{center}
		\includegraphics[width=0.48\textwidth]{./figures/results/varying_rotation}
	\end{center}
	\caption{\textbf{Caption:} Caption.
	\label{fig:varying_rotation}}
\end{figure}

@@

% Esta figura deberia tener 3 x 3 vinetas. vrot=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vout=25, | tau=1E5, vout=50, | tau=1E5, vout=75,
% |tau=1E6, vout=25, | tau=1E6, vout=50, | tau=1E6, vout=75,
% |tau=1E7, vout=25, | tau=1E7, vout=50, | tau=1E7, vout=75, 
\begin{figure}
	\begin{center}
		\includegraphics[width=0.48\textwidth]{./figures/results/varying_outflow}
	\end{center}
	\caption{\textbf{Caption:} Caption.
		\label{fig:varying_outflow}}
\end{figure}

@@

% Esta figura deberia tener 3 x 2 viñetas. tau=10E5.
% cada panel tiene una curva para no rotation, rotation (radiative transfer)
% y rotation (doppler)
% |vrot=50, vout=5,  | vrot=100, vout=5,  |
% |vrot=50, vout=25, | vrot=100, vout=25, |
% |vrot=50, vout=50, | vrot=100, vout=50, |
\begin{figure}
	\begin{center}
		\includegraphics[width=0.48\textwidth]{./figures/results/doppler_shift}
	\end{center}
	\caption{\textbf{Caption:} Caption.
		\label{fig:doppler_shift}}
\end{figure}

>>>>

In this paper we introduce first our theoretical tools and assumptions
in Section \ref{sec:theory}. We continue in Section  \ref{sec:results}
with the results from the Monte-Carlo simulation, the comparison
against the semi-analytical approximation which we use to make a
thorough exploration of the effect of rotation.
In Section \ref{sec:discussion} we discuss our results and their
possible implications for observational analysis to finally present
our conclusions in Section \ref{sec:conclusions}.

@@

% Esta figura deberia tener 3 x 3 vinetas. vout=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vrot=0, | tau=1E5, vrot=50, | tau=1E5, vrot=100, 
% |tau=1E6, vrot=0, | tau=1E6, vrot=50, | tau=1E6, vrot=100, 
% |tau=1E7, vrot=0, | tau=1E7, vrot=50, | tau=1E7, vrot=100, 
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/varying_rotation}
	\end{center}
	\caption{\textbf{Caption:} Caption.
	\label{fig:varying_rotation}}
\end{figure*}

@@

% Esta figura deberia tener 3 x 3 vinetas. vrot=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vout=25, | tau=1E5, vout=50, | tau=1E5, vout=75,
% |tau=1E6, vout=25, | tau=1E6, vout=50, | tau=1E6, vout=75,
% |tau=1E7, vout=25, | tau=1E7, vout=50, | tau=1E7, vout=75, 
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/varying_outflow}
	\end{center}
	\caption{\textbf{Caption:} Caption.
		\label{fig:varying_outflow}}
\end{figure*}

@@

% Esta figura deberia tener 3 x 2 viñetas. tau=10E5.
% cada panel tiene una curva para no rotation, rotation (radiative transfer)
% y rotation (doppler)
% |vrot=50, vout=5,  | vrot=100, vout=5,  |
% |vrot=50, vout=25, | vrot=100, vout=25, |
% |vrot=50, vout=50, | vrot=100, vout=50, |
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift}
  \end{center}
  \caption{\textbf{Caption:} Caption.
    \label{fig:doppler_shift}}
\end{figure*}
